---
title: "Team.Rmd"
author: "Muhamad Imran Bin Maszeri and Dongming Li"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rating vs. Company

    We try to find which companies can make the best chocolate in the world.
```{r echo=TRUE}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
COMPANY<-factor(choco$Company)
lvl1<-levels(COMPANY)
TYPE1<-reorder(COMPANY,choco$Rating,FUN = mean)
TYPE1<-sort(TYPE1,decreasing = TRUE)
TYPE1<-factor(TYPE1,levels(TYPE1)[541:1])
lvl2<-levels(TYPE1)
head(lvl2,n=10)
```
    
    This list is the TOP 10 chocolate companies based on their average rating.
```{r echo=FALSE}
TOBAGO<-choco[choco$Company=='Tobago Estate (Pralus)',]
OCELOT<-choco[choco$Company=='Ocelot',]
HEIRLOOM<-choco[choco$Company=='Heirloom Cacao Preservation (Zokoko)',]
MATALE<-choco[choco$Company=='Matale',]
PATRIC<-choco[choco$Company=='Patric',]
IDILIO<-choco[choco$Company=='Idilio (Felchlin)',]
UTOPICK<-choco[choco$Company=='Utopick',]
DIMANCHE<-choco[choco$Company=='Un Dimanche A Paris',]
TIMO<-choco[choco$Company=='Timo A. Meyer',]
OBOLO<-choco[choco$Company=='Obolo',]
TOBAGO1<-mean(TOBAGO$Rating)
OCELOT1<-mean(OCELOT$Rating)
HEIRLOOM1<-mean(HEIRLOOM$Rating)
MATALE1<-mean(MATALE$Rating)
PATRIC1<-mean(PATRIC$Rating)
IDILIO1<-mean(IDILIO$Rating)
UTOPICK1<-mean(UTOPICK$Rating)
OBOLO1<-mean(OBOLO$Rating)
DIMANCHE1<-mean(DIMANCHE$Rating)
TIMO1<-mean(TIMO$Rating)
GROUP<-c(TOBAGO1,OCELOT1,HEIRLOOM1,MATALE1,PATRIC1,IDILIO1,UTOPICK1,DIMANCHE1,TIMO1,OBOLO1)
names(GROUP)<-c('Tobago Estate (Pralus)','Ocelot','Heirloom Cacao Preservation (Zokoko)','Matale','Patric','Idilio (Felchlin)','Utopick','Un Dimanche A Paris','Timo A. Meyer','Obolo')
barplot(GROUP,ylim = c(0,4.0),las=2)
GROUP
```
    
    From the chart and data we can see that the top 10 chocolate companies in the world all have ratings above 3.75. This suggests that chocolate produced from these companies is highly recommended. And in our analysis, we found that these companies did not have many products rated, but as long as the products were rated, the ratings were very high. This shows that these companies pay great attention to the quality of chocolate.




## Rating vs. Bean origin (Or any other analysis you want do)